[![Travis-CI Build Status](https://travis-ci.org/codyschulz/robustGeocode.svg?branch=master)](https://travis-ci.org/codyschulz/robustGeocode)

# robustGeocode

`robustGeocode` allows users to conveniently overcome Google Maps geocoding API problems.

## Installation
`robustGeocode` can be installed using `devtools`:
```{r devtools, eval = FALSE}
library(devtools)
install_github("codyschulz/robustGeocode")
library(robustGeocode)
```

## `geocode_robust()`

`robustGeocode` contains a single function, `geocode_robust()`, which geocodes locations until all are geocoded. Normal geocoding with the `ggmaps` `geocode()` function currently has an extremely high failure rate, as we can see below.

```{r geocode_failure, warning = FALSE, message = FALSE}
library(ggmap)
data <- data.frame(addr = c("The White House", "11 Wall St, New York, NY", "525 A St. NE, Washington, DC", "42 Wallaby Way, Sydney"), 
                   stringsAsFactors = FALSE)
geocode(data$addr)
```

`geocode_robust()` geocodes the (unique) locations provided, then geocodes again the locations that failed to geocode. It repeats this 10 times or until all observations have latlons (whichever comes first).
```{r geocode_robust, message = FALSE}
library(robustGeocode)
geocode_robust(data, "addr")
```

Users can also specify the number of times to repeat the geocoding process
```{r choose_n, message = FALSE}
geocode_robust(data, "addr", 3)
```

`geocode_robust()` merges the unique locations and latlons back onto the original dataset so no observations are lost. It also maintains the original observation order
```{r dup_addresses}
data_add <- rbind(data, data[1,])
data_add
geocode_robust(data_add, "addr")
```

Users can also specify whether they want their original dataset with the lat and lon columns returned (`return_full_dataframe` = TRUE) or just want the lat and lon columns (`return_full_dataframe` = FALSE - the default).
```{r return_full_dataframe`}
geocode_robust(data, "addr", return_full_dataframe = TRUE)
```
